---
title: "Assignment 5"
author: "Yedhu Sanil Kumar"
date: "10/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## Enhancing the productivity of hybrid Poplar (Populus× hybrid) and Switchgrass (Panicum virgatum L.) by the application of beneficial soil microbes and a seaweed extract.

Fei, H., Crouse, M., Papadopoulos, Y., & Vessey, J. K. (2017). Enhancing the productivity of hybrid Poplar (Populus× hybrid) and Switchgrass (Panicum virgatum L.) by the application of beneficial soil microbes and a seaweed extract. Biomass and bioenergy, 107, 122-134.

https://github.com/Yedhu89/Assisgnment_5_Yedhu.git

## Introduction:

The study by Fei et al.,(2017) carries out an investigation on the effects of three beneficial soil microbes Azospirillum brasilense, Pencillium bilaii, Variovorax paradoxus, and Ascophyllum nodosum (Seaweed) tested on the growth of three clones of hybrid poplars and two cultivars of Switchgrass grown under greenhouse conditions and on marginal land. 
Good quality and high yielding feedstocks on marginal lands with low inputs could help lower costs.Beneficial soil microbes have many advantages to plants like enhanced growth, at low costs (Vessey, J. K. 2003). Inoculating biofuel feedstock crop species with such microbes can increase the productivity and lower the costs of biofuel feedstocks.This experiment was done to enhance to yield and productivity of the biomass crops by the application of beneficial soil microbes and a seaweed. The application of beneficial soil microbes and plant supplements enhances productivity of biomass feedstocks and help lower cost of biofuel.
```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
